An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-07-13 EconGrowth.Rnw
Now using rewritten sfResamplePlot for all SF resample graphs.

<<LINEXq_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="LINEX model (with $q$) resampling results." >>=
linexResamplePlot(energyType="Q")
@

>>>>

<<LINEXq_Resample_Graph, fig.pos="H", fig.width=ninePanelGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="LINEX model (with $q$) resampling results.">>=
# linexResamplePlot(energyType="Q")
linexResamplePlot(energyType="Q")
@
